### 2023-08-12 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel. We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus. The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space. However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}). For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.  In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the confinement ratio increases to a maximum of $2$ at the neck. Consequently the dependence of the vesicle shape on the capillary number is expected to be less sensitive according to results in \citet{aga-bir2020}. Finally the phase separation is assumed to occur at a much faster time scale than vesicle relaxation with Peclet number $Pe=1$.

As a multicomponent vesicle enters/leaves a closely-fitted stenosis, coarsening of the lipid domains is expedited. However, inside the stenosis, the strong confinement hinders the coarsening as both the vesicle shape and the lipid domains remain more or less un-altered as the vesicle moves through the stenosis. Once inside a stenosis, we define the lubrication layer and its corresponding width to analyze the mechanical coupling between the boundaries in lipid domain and the planar shear flow inside the lubrication layer, which consists of a quadratic component (due to pressure gradient in the thin film) and a linear component (due to membrane motion in the tangential direction). By analyzing these two components at various locations in the lubrication layer, we first identified that tank treading along the vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer width on the two sides.  We further elucidated  the correlation between the location of boundary between lipid domains, the Marangoni stress,  and the change of sign in the pressure gradient in the lubrication layer. These results may be used to identify the lipid domains via the visualization of the flow in the lubrication layer.

>>>>

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics
of a multicomponent vesicle under strong confinement, which is a
ubiquitous configuration in biology when a cell squeezes through a small
channel. We refined the phase-field formulation
in~\citet{liu-mar-li-vee-low2017} with a new bending model that uses a
sigmoidal function for the bending stiffness to retain positiveness in
the bending modulus. The linear model~\cite{liu-mar-li-vee-low2017}
works well for a vesicle in free-space. However, under strong
confinement we find it necessary to enforce the condition that the
dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$
($\beta = b_{\min}/b_{\max}$) to avoid instability in membrane shapes
(see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a
multicomponent vesicle in two types of confinement: a stenosis channel
(\S~\ref{subsec:Stenosis}), and a contracting channel
(\S~\ref{subsec:Contraction}). For both confining geometries we varied
the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and
the initial distribution of lipid domains with a fixed Capillary number
$Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$. In
\S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
confinement ratio increases to a maximum of $3.60$ at the neck.
Consequently the dependence of the vesicle shape on the capillary number
is expected to be less sensitive according to results
in~\citet{aga-bir2020}. Finally the phase separation is assumed to occur
at a much faster time scale than vesicle relaxation with Peclet number
$Pe=1$.

As a multicomponent vesicle enters/leaves a closely-fitted stenosis,
coarsening of the lipid domains is expedited. However, inside the
stenosis, the strong confinement hinders the coarsening as both the
vesicle shape and the lipid domains remain more or less unaltered as the
vesicle moves through the stenosis. Once inside a stenosis, we define
the lubrication layer and its corresponding width to analyze the
mechanical coupling between the boundaries in lipid domain and the
planar shear flow inside the lubrication layer, which consists of a
quadratic component (due to pressure gradient in the thin film) and a
linear component (due to membrane motion in the tangential direction).
By analyzing these two components at various locations in the
lubrication layer, we first identified that tank treading along the
vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer
width on the two sides. We further elucidated the correlation between
the location of boundary between lipid domains, the Marangoni stress,
and the change of sign in the pressure gradient in the lubrication
layer. These results may be used to identify the lipid domains via the
visualization of the flow in the lubrication layer.
